Constraints on the mass and occupation fraction of dark matter halos hosting Lyman-alpha emitters at $z\sim 3$

### 2013-07-29 paper/ms.tex
updated section on ACF

The second constraint is the angular correlation function (ACF). The
measurements presented in \citep{Yamada2012} do not report an ACF
measurement. Instead we use the results reported by
\citep{Hayashino2004} on the LAEs observed in the densest field of
SSA22. It is important to keep in mind that there are some differences
between this work and \citep{Yamada2012}. First, the color selection by
\cite{Yamada2012} is less stringent compared to the one by
\cite{Hayashino2004}. Also the EW threshold is different,
\cite{Hayashino2004} uses a cut around $154$\AA \ instead of $190$\AA
\ used by \citep{Yamada2012}. These differences  translates
in only two more detected objects in the Hayashino survey (283 LAEs) than in 
Yamada et al (281 LAEs).

@@

The Bolshoi simulation \citep{Bolshoi} we use in this paper was
performed in a cubic volume of 250 $h^{-1}$ Mpc on a side. It includes
dark matter distribution is sampled using $2048^{3}$ particles, which
translates into a particle mass of $m_{\rm   p}=1.35\times 10^{8}$
$h^{-1}$ M$_{\odot}$.  The cosmological parameters are consistent with
a WMAP5 and WMAP7 data with a  density $\Omega_{\rm m} = 0.27$,
cosmological  $\Omega_{\Lambda}=0.73$, dimensionless Hubble constant
$h=0.70$, slope of the power spectrum $n=0.95$ and normalization of the
power spectrum$\sigma_{8}=0.82$ \citep{Komatsu2009,Jarosik2011}.

We use halo catalogs constructed with a Friend-of-Friends (FOF)
algorithm with a linking length of 0.17 times the inter-particle
distance. The minimum halo mass in the models we construct in this \documentname
correspond to groups of $\sim 75$ particles. The catalogs were
obtained from the publicly available Multidark database \footnote{{\tt
    http://www.multidark.org/MultiDark/}} \citep{2011arXiv1109.0003R}.
We focus our work on halos more massive than $1\times 10^{10}$\hMsun
that are resolved with at least $70$ particles ({\bf REFF???? or support???})

@@

In our model a dark matter halo can only host one or zero LAE. 
There are three parameters in the model that decide whether a halo can host a
galaxy or not: the lower and upper bounds for the mass range $M_{\rm min}<
M_{\rm h} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
  occ}$ of such halos that host a \emph{detectable LAE}. The reader
must keep in mind that the physical interpreation of the occupation
fraction $f_{\rm occ}$ convolves two things: the presence of a star
forming galaxy in a halo and its detectability as a LAE. We do not assign a
luminosity to each LAE. We are primarily interested in
constraining the halo mass range hosting detectable LAEs under the
conditions defined by \cite{Yamada2012}. In what follows we will describe by
the letter ${\mathcal M}$ a model defined by an specific choice of the
three scalar parameters $M_{\rm min}$, $M_{\rm  max}$ and $f_{\rm occ}$.

@@

Next we construct mock surveys by making groups of $11$ mock fields
out of the $210$ available volumes. In total $15$ mock surveys are
constructed for each model $\mathcal{M}$. The grouping is done in two
different ways. In the first way, called {\texttt match}, we follow
the clustering of the observed fields. From the $11$ mock fields, $7$
are constructed from contiguous fields in the simulation to mimic the
SSA22 region, $3$ are also contiguous between them but not to the first
$7$ fields to mimic the SXDS fields and finally $2$ non-contiguous
fields to imitate the SDF and GOODS-North field. Our main goal with
this selection is to test the impact on the final statistics of having
$7$ clustered fields. The second way to group the mock fields is called {\texttt
  random}, whereby all the $11$ fields are selected in such a way as
to avoid that any two volumes are contiguous.

@@

\begin{equation}
\xi(\theta) = \left(\frac{\theta}{\theta_{0}}\right)^{\gamma}
\label{eq:fitting}
\end{equation}

Both mock and observational ACF are derived by a least
square minimization procedure. The observational errors of 
the ACF as well as the standard deviation of the mean modelled ACFs  are
considered to compute the error in the fitted parameters to ensure ourselves
to include poissionian and cosmic-variance errors. 
We consider that a model is consistent with observations if the two parameters $\gamma$ and $\theta_0$ are
equal within a $1$-$\sigma$ range.

@@

\subsection{Surface density distributions}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf} 
\hspace{5mm}  
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf} 
\end{center}
\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\gamma$) 
in the fitting formula (Eq. \ref{eq:fitting}) for the mean angular
correlation function. Blue dots correspond to simulations and the green cross to
observations by \citet{Hayashino2004}. The error bars in the 
theoretical data correspond to the standard deviation from the
different mocks surveys. Right: Same results as before in the shown in
the $\theta_{0}$-$M_{\rm min}$ plane. This time the observational
constraints are represented by the red rectangle. Blue squares
represent models with $\log_{10} M_{\rm  max}<12.0$, green circles
correspond to models with $\log_{10} M_{\rm max}>12.0$. 
\label{figure:correlation_parameters}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_mmax.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_focc.pdf}
\end{center}
\caption{Best models parameter space when both the constraints on the
  maximal number of  consistent mocks and the occupation  fraction
  $f_{\rm occ}\leq  0.2$ are included. $M_{\rm min}$ vs $M_{\rm max}$
  (left), $M_{\rm min}$ vs $f_{\rm occ}$ (rigth).
  \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*}

Figure \ref{figure:correlation_parameters} shows the main results in a
$\theta_{0}-\gamma$  plane where the average and standard deviation
for each mock is shown in comparison with the result derived from
observations.  The error bars in this Figure represents the standard
deviation of the ACF over all the sub-fields in the 15 mock
observations. These error bars are larger than the statistical
uncertainty from the fitting procedure on a single field.

@@

In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
for the {\tt match} method after applying the observational constraints 
in the occupation fraction and the ACF. Here we consider a model
consistent if there is an overlap of $1-\sigma$ in its values for the
correlation length $\theta_0$ and the power $\gamma$ in the
correlation function.  As before, we found similar results using the {\tt random} method

@@

... \cite{Ouchi2010} prefers a very lowe duty cycle $0.008\pm 0.03$.

@@

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
10.1& 10.2& 0.1\\
10.3& 10.5& 0.1\\
10.4& 10.7& 0.1\\
10.5& 10.6& 0.3\\
10.5& 10.9& 0.1\\
10.5& 11.0& 0.1\\
10.6& 10.8& 0.2\\
10.6& 11.2& 0.1\\
10.6& 11.3& 0.1\\
10.6& 11.4& 0.1\\
10.6& 11.5& 0.1\\
10.6& 11.6& 0.1\\
10.7& 11.0& 0.2\\
10.8& 11.2& 0.2\\
10.8& 11.3& 0.2\\
10.8& 11.4& 0.2\\
10.9& 11.3& 0.3\\
10.9& 11.7& 0.2\\
10.9& 11.8& 0.2\\
10.9& 11.9& 0.2\\
11.0& 11.6& 0.3\\
11.0& 11.7& 0.3\\
11.0& 11.8& 0.3\\
11.0& 12.0& 0.3\\\hline\hline
\end{tabular}
\end{center}
\caption{\label{table:thirdfamily}List of parameters for the first
  family of models. Narrow   mass range $\Delta M\leq 1.0$dex and low
  occupation fraction $f_{\rm occ}\leq 0.3$.} 
\end{table}

>>>>

The second constraint is the angular correlation function
(ACF). \cite{Yamada2012} does not report an ACF measurement. Instead
we use the results by \cite{Hayashino2004} and
\cite{Ouchi2008,Ouchi2010}.

\cite{Hayashino2004} observed in the densest field of
SSA22 while \cite{Ouchi2008} observed on a 1 deg$^2$ sky of the
Subaru/XMM-Newton Deep Survey (SXDS) Field.  There are some
differences between these observations and those iby
\cite{Yamada2012}. The details in the color selection, corresponding
limiting luminosities and EW thresholds are different in these
references. Nevertheless we use these observations as additional
constraints in spite of the fact that the first selected models are
based only on the surface density statistics by \citep{Yamada2012}.

@@

The Bolshoi simulation \citep{Bolshoi} we use in this paper was
performed in a cubic volume of 250 $h^{-1}$ Mpc on a side. The
dark matter distribution is sampled using $2048^{3}$ particles, which
translates into a particle mass of $m_{\rm   p}=1.35\times 10^{8}$
$h^{-1}$ M$_{\odot}$.  The cosmological parameters are consistent with
a WMAP5 and WMAP7 data with a matter density $\Omega_{\rm m} = 0.27$,
cosmological constant $\Omega_{\Lambda}=0.73$, dimensionless Hubble constant
$h=0.70$, slope of the power spectrum $n=0.95$ and normalization of the
power spectrum$\sigma_{8}=0.82$ \citep{Komatsu2009,Jarosik2011}.

We use halo catalogs constructed with a Friend-of-Friends (FOF)
algorithm with a linking length of 0.17 times the inter-particle
distance. The catalogs were obtained from the publicly available
Multidark database \footnote{{\tt
    http://www.multidark.org/MultiDark/}}
\citep{2011arXiv1109.0003R}. We focus our work on halos more massive
than $1\times 10^{10}$\hMsun that are resolved with at least $70$
particles, the reasons for this choice are explained in the next
section.

@@

In our model a dark matter halo can only host one LAE at most. 
There are three parameters in the model that decide whether a halo can host a
galaxy or not: the lower and upper bounds for the mass range $M_{\rm min}<
M_{\rm h} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
  occ}$ of such halos that host a \emph{detectable LAE}. The reader
must keep in mind that the physical interpreation of the occupation
fraction $f_{\rm occ}$ convolves two things: the presence of a star
forming galaxy in a halo and its detectability as a LAE. We do not assign a
luminosity to each LAE. We are primarily interested in
constraining the halo mass range hosting detectable LAEs under the
conditions defined by \cite{Yamada2012}. In what follows we will describe by
the letter ${\mathcal M}$ a model defined by an specific choice of the
three scalar parameters $M_{\rm min}$, $M_{\rm  max}$ and $f_{\rm occ}$.

@@

Next we construct mock surveys by making groups of $11$ mock fields
out of the $210$ available volumes. In total $15$ mock surveys are
constructed for each model $\mathcal{M}$. The grouping is done in two
different ways. In the first way, called {\texttt match}, we follow
the clustering of the observed fields. From the $11$ mock fields, $7$
are constructed from contiguous fields in the simulation to mimic the
SSA22 region, $3$ are also contiguous between them but not to the first
$7$ fields to mimic the SXDS fields and finally $2$ non-contiguous
fields to imitate the SDF and GOODS-North field. Our main goal with
this selection is to test the impact on the final statistics of having
$7$ clustered fields. The second way to group the mock fields is called {\texttt
  random}, whereby all the $11$ fields are selected in such a way as
to avoid that any two volumes are contiguous. In this \documentname we
only report the results obtained by the {\texttt match} method that
are also obtained in the {\texttt random} selection.

@@

\begin{equation}
\omega(\theta) = \left(\frac{\theta}{\theta_{0}}\right)^{-\beta}
\label{eq:fitting}
\end{equation}

Both mock and observational ACF are derived by a least
square minimization procedure. The observational errors of 
the ACF as well as the standard deviation of the mean modelled ACFs  are
considered to compute the error in the fitted parameters to ensure ourselves
to include poissionian and cosmic-variance errors. 
We consider that a model is consistent with observations if the two parameters $\beta$ and $\theta_0$ are
equal within a $1$-$\sigma$ range.

@@

\subsection{Models consistent with the surface density distributions}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf} 
\hspace{5mm}  
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf} 
\end{center}
\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\beta$) 
in the fitting formula (Eq. \ref{eq:fitting}) for the mean angular
correlation function. Blue dots correspond to simulations and the green cross to
observations by \citet{Hayashino2004}. The error bars in the 
theoretical data correspond to the standard deviation from the
different mocks surveys. Right: Same results as before in the shown in
the $\theta_{0}$-$M_{\rm min}$ plane. This time the observational
constraints are represented by the red rectangle. Blue squares
represent models with $\log_{10} M_{\rm  max}<12.0$, green circles
correspond to models with $\log_{10} M_{\rm max}>12.0$. 
\label{figure:correlation_parameters}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_f_occ.pdf}
\end{center}
\caption{Best models parameter space when both the constraints on the
  maximal number of  consistent mocks and the occupation  fraction
  $f_{\rm occ}\leq  0.2$ are included. $M_{\rm min}$ vs $M_{\rm max}$
  (left), $M_{\rm min}$ vs $f_{\rm occ}$ (rigth).
  \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*}

Figure \ref{figure:correlation_parameters} shows the main results in a
$\theta_{0}-\beta$  plane where the average and standard deviation
for each mock is shown in comparison with the result derived from
observations.  The error bars in this Figure represents the standard
deviation of the ACF over all the sub-fields in the 15 mock
observations. These error bars are larger than the statistical
uncertainty from the fitting procedure on a single field.

@@

In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
for the {\tt match} method after applying the observational constraints 
in the occupation fraction and the ACF. Here we consider a model
consistent if there is an overlap of $1-\sigma$ in its values for the
correlation length $\theta_0$ and the power $\beta$ in the
correlation function.  As before, we found similar results using the {\tt random} method

@@

\cite{Ouchi2010} presents an analysis of LAE observations in the
redshift interval $3.1<z<7.0$. At $z=3.1$ They get to an average
mass for the host dark matter halos of $M_{h}=2.9^{+24.0}_{-2.9}\times
10^{10}$ \hMsun with a corresponding duty cycle of $0.008\pm
0.03$. This broadly matches the expectations from the first family of
models, also summarized in Table \ref{table:firstfamily}. In
particular it seems to favor only the very low occupations fractions.

@@

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
10.1& 10.2& 0.1\\
10.3& 10.5& 0.1\\
10.4& 10.7& 0.1\\
10.5& 10.6& 0.3\\
10.5& 10.9& 0.1\\
10.5& 11.0& 0.1\\
10.6& 10.8& 0.2\\
10.6& 11.2& 0.1\\
10.6& 11.3& 0.1\\
10.6& 11.4& 0.1\\
10.6& 11.5& 0.1\\
10.6& 11.6& 0.1\\
10.7& 11.0& 0.2\\
10.8& 11.2& 0.2\\
10.8& 11.3& 0.2\\
10.8& 11.4& 0.2\\
10.9& 11.3& 0.3\\
10.9& 11.7& 0.2\\
10.9& 11.8& 0.2\\
10.9& 11.9& 0.2\\
11.0& 11.6& 0.3\\
11.0& 11.7& 0.3\\
11.0& 11.8& 0.3\\
11.0& 12.0& 0.3\\\hline\hline
\end{tabular}
\end{center}
\caption{\label{table:firstfamily}List of parameters for the first
  family of models. Narrow   mass range $\Delta M\leq 1.0$dex and low
  occupation fraction $f_{\rm occ}\leq 0.3$.} 
\end{table}
